Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials

### 2022-11-04 study protocol.qmd
Updated Quarto Markdown

---
title: "Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials"
subtitle: "Study Protocol and Statistical Analysis Plan"
author: "Nikhil Patel, MD"
format: docx
---

@@

Patients with neurological injury experience different symptoms between the left and right hemispheres, and this may have.

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)

@@

```{r ATACH2, include=FALSE}

@@

```{r ERICH, include=FALSE}

@@

```{r combining ATACH2 and ERICH, include=FALSE}

@@

>>>>

---
title: "Hemispheric Lateralization and Outcomes After ICH: A Pooled Analysis of Clinical Trials"
subtitle: "Study Protocol"
author: "Nikhil Patel, MD"
format: 
  html:
    toc: true
    toc-location: left
    toc-title: ""
    css: styles.css
    anchor-sections: true
    code-fold: true
    code-overflow: wrap
    code-summary: "Show the code"
    output: false
---

@@

Patients with neurological injury experience different symptoms between the left and right hemispheres. This may affect prognostic estimates, and how frequently patients are offered aggressive care. In this study, we aimed to investigate any differential treatment patterns based on hemispheric lateralization, as well as differences in outcome with a pooled analysis of NINDS randomized trials enrolling patients with ICH.

@@

**Loading packages and data and define helper functions**

```{r Initial Setup}

library(tidyverse)
library(tableone)
library(data.table)
library(haven) # Importing SAS Files
library(janitor)
library(lubridate)

@@

**Importing and wrangling ATACH2 data

```{r ATACH2}

@@

Importing and wrangling ERICH data

```{r ERICH}

@@

Combining Datasets

```{r combining ATACH2 and ERICH}

@@

table1 <- CreateTableOne(data = atach.erich,
                         strata = "ich.laterality",)

print(table1, showAllLevels = FALSE)
